---
title: "COVID-19 Review and Meta-Analysis"
author: "Vicente Ramirez"
date: "6/5/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE}
require(tidyverse)
require(magrittr)
require(meta)
require(metaviz)
require(readxl)
```

## Removing Unnecessary Data
```{r cache=TRUE}
dat<-read_excel("Review_Data.xlsx")
dat %<>%
  filter(`RH Include?`=="YES")
##We dedcided to filter this becuase it was not in english
dat %<>% filter(`Author Name`!= "Bocksberger et al.")
COVID19 <- dat %>% select(`Article Number`,`Author Name`,DOI,`Number of subjects`,Cases,Type,Measured)
write_csv(COVID19,"COVID19_REVIEW_DATA_.csv")
rm(dat)
```

## Compute some statistics
```{r fig.height = 6, fig.width = 12, cache=TRUE}
COVID19$p<- COVID19$Cases/COVID19$`Number of subjects`

COVID19$S.E.<- sqrt((COVID19$p*(1-COVID19$p))/COVID19$`Number of subjects`)
COVID19$CI_Lower<-COVID19$p - 1.96*COVID19$S.E.
COVID19$CI_Upper<- COVID19$p + 1.96*COVID19$S.E.
COVID19 <- COVID19[order(COVID19$p,decreasing = T),]
summary_COVID_Obj<-data.frame(Name="Summary (Objective)",Subjects=sum(COVID19[COVID19$Type=="Objective","Number of subjects"]),Cases=sum(COVID19[COVID19$Type=="Objective","Cases"]))
summary_COVID_Sub<-data.frame(Name="Summary (Subjective)",Subjects=sum(COVID19[COVID19$Type=="Subjective","Number of subjects"]),Cases=sum(COVID19[COVID19$Type=="Subjective","Cases"]))

summary_COVID<-bind_rows(summary_COVID_Obj,summary_COVID_Sub)
COVID19$`Measure Type`<-as.factor(COVID19$Type)
```

## Computing Detailed Meta-Analysis of Proportions

### IVM
First we compute using the Inverse Variance Method
```{r fig.align = "center", fig.height = 10.5, fig.width = 9.5, cache=TRUE}
ma.INV<-metaprop(COVID19$Cases,n=COVID19$`Number of subjects`,studlab = COVID19$`Author Name`,byvar = COVID19$`Measure Type`,data=COVID19, method="Inverse",sm="PFT", method.ci = "WS")
d=date()
#pdf(sprintf("Forestplot_%s",d))
forest(ma.INV,col.by = "black",pooled.events = T,bylab = "Measurement Type")
#dev.off()
```

###GLMM
Next we compute using the GLMM method. We ultimately do no use this in the paper.
```{r fig.align = "center", fig.height = 10.5, fig.width = 9.5, cache=TRUE}
ma.GLMM<-metaprop(COVID19$Cases,n=COVID19$`Number of subjects`,studlab = COVID19$`Author Name`,byvar = COVID19$`Measure Type`,data=COVID19, method.ci = "WS")

forest(ma.GLMM,,col.by = "black",pooled.events = T,bylab = "Measurement Type")
```


##Flow Chart
This code was adapted from Peter Higgins post on https://rpubs.com/phiggins/461686
```{r cache=TRUE}
data <- tibble(x= 1:100, y= 1:100)
head(data)

p<- data %>% 
  ggplot(aes(x, y)) +
  scale_x_continuous(minor_breaks = seq(0, 100, 10)) +
  scale_y_continuous(minor_breaks = seq(0, 100, 10)) +
  theme_linedraw()

p <- p +
  geom_rect(xmin = 36, xmax=64, ymin=90, ymax=100, color='black',
            fill='white', size=0.25, size=0.25) +
  annotate('text', x= 50, y=95,label=
             'Assessed for eligibility through database\n searching (Pubmed, Medline, Google Scholar).\n Performed 5/15/2020 N=78',
           size=2.5)
p<- p +
  geom_rect(xmin = 75, xmax=100, ymin=80, ymax=90, color='black',
            fill='white', size=0.25, size=0.25) +
  annotate('text', x= 87, y=85,label=
             'Excluded N=35 \n Not meeting inclusion criteria or data unavailable \n Not written in the English language',
           size=2.5)
```
##HERE IS ESSENTIALLY WHAT WE ARE DOING RIGHT NOW.
It is ugly for now, but this is the thought process behind the code
```{r fig.width=12, fig.height=8, cache=TRUE}
p
```

##Final Version
```{r fig.width=12, fig.height=8, cache=TRUE}
p<- p +
  geom_rect(xmin = 36, xmax=64, ymin=70, ymax=80, color='black',
          fill='white', size=0.25, size=0.25) +
  annotate('text', x= 50, y=75,label=
            'Eligible papers for inclusion \nMeasure of olfactory dysfunction \nN=43',
             size=2.5)

p <- p +
  geom_rect(xmin = 75, xmax=100, ymin=60, ymax=70, color='black',
          fill='white', size=0.25, size=0.25) +
  annotate('text', x= 87, y=65,label=
             'Excluded \n Not lab tested COVID N=5\n Recruitment of Patients With Smell Loss N=3 \n Papers with Overlapping Samples N=1',
           size=2.5)
p<- p +
  geom_rect(xmin = 36, xmax=64, ymin=50, ymax=60, color='black',
            fill='white', size=0.25, size=0.25) +
  annotate('text', x= 50, y=55,label=
             'Full text screened for prevalence rate \nN=34',
           size=2.5)

p<- p +
  geom_rect(xmin = 36, xmax=64, ymin=30, ymax=40, color='black',
            fill='white', size=0.25, size=0.25) +
  annotate('text', x= 50, y=35,label=
             ' Data extracted N=34 \nTwo authors extracted data \nTwo authors confirmed data extracted',
           size=2.5)

p<- p +
  geom_rect(xmin = 36, xmax=64, ymin=10, ymax=20, color='black',
            fill='white', size=0.25, size=0.25) +
  annotate('text', x= 50, y=15,label=
             'Articles included \nN=34',
           size=2.5)


p <-p +
  geom_segment(
    x=50, xend=50, y=90, yend=80.3, 
    size=0.10, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=74.7, y=85, yend=85, 
    size=0.10, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=50, y=70, yend=60.3, 
    size=0.10, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=74.7, y=65, yend=65, 
    size=0.10, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=50, y=50, yend=40.3, 
    size=0.10, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=50, y=30, yend=20.3, 
    size=0.10, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed"))


p + theme_void()
```
